---
title: "Svalbard Midtre Lovenbreen -- Patch Study"
subtitle: "Alpha Diversity - 18S SSU rRNA gene"
author: "Adam J. Solon"
date: "`r Sys.Date()`"
#output: html_document
output: 
  pdf_document:
    toc: TRUE
    fig_width: 7
    fig_height: 6
    fig_caption: true
fontsize: 12pt
#editor_options: 
#  chunk_output_type: console
---

# Script Summary  
This script calculates and compares the richness, Shannon diversity, and Pielou evenness of communities of microeukaryotes (18S) across sediments in biocrust and bare surface patches in a glacial forefield chronosequence.


### Steps of this pipeline:  
1.  Create and organize directories
2.  Load R packages
3.  Input files
4.  Format Files
5.  Richness
6.  Shannon
7.  Save files and figures
  
```{r echo = FALSE, include = FALSE, set.seed(461)}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(include = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = TRUE)

```

# Begin pipeline

### Set paths for Taxonomic Summary analyses  
```{r, echo = FALSE, include = FALSE}
# Change identifiers to your system and file naming
user <- "F:"
folder <- "/Projects"
project <- "/Sunspears"
study <- "/Studies"
files <- "/Patch_Schmidt-et-al"

directory.1 <- "/analyses/amplicons/18s"

analysis.1 <- "/alpha_diversity"

ecosystem <- "glacial forefield - Svalbard" # Define the environment for use in report language.

```

```{r set paths for pipeline}
# First define the project and project folders. 

# Create pathway for pipeline
###################################################
path.fp <- paste0(user, folder, project, study, files)
if (!dir.exists(path.fp)) dir.create(path.fp)

```

```{r set path for analyses}
#directory.1
###################################################
directory.1.fp <- paste0(path.fp, directory.1)
if (!dir.exists(directory.1.fp)) dir.create(directory.1.fp)

# Create sub-directory  analysis.1
###################################################
analysis.1.fp <- paste0(directory.1.fp, analysis.1)
if (!dir.exists(analysis.1.fp)) dir.create(analysis.1.fp)

# Create sub-directories for analysis 
###################################################

# Create directory for 'within' pipeline R objects 
objects.fp <- paste0(analysis.1.fp, "/objects")
if (!dir.exists(objects.fp)) dir.create(objects.fp, recursive = TRUE)

# Create directory for 'after' pipeline outputs 
output.fp <- paste0(analysis.1.fp, "/output")
if (!dir.exists(output.fp)) dir.create(output.fp, recursive = TRUE)

# Create directory for 'after' pipeline outputs 
sub.1.fp <- paste0(output.fp, "/stats")
if (!dir.exists(sub.1.fp)) dir.create(sub.1.fp, recursive = TRUE)

# Create directory for 'after' pipeline outputs 
sub.2.fp <- paste0(output.fp, "/plots")
if (!dir.exists(sub.2.fp)) dir.create(sub.2.fp, recursive = TRUE)

# Check for the folders here as a sanity check. Should see "Input" and "Objects" if starting from scratch.
list.files(analysis.1.fp) 

```

### Session Information  
```{r Install and load packages}
# install.packages("tidyverse")
# install.packages("knitr")
# install.packages("kableExtra")
# install.packages("reshape2")
# install.packages("vegan")
# install.packages("phyloseq")
# install.packages("FSA")
# install.packages("multcomp")
# install.packages("multcompView")
# install.packages("grDevices")
# install.packages("gratia")

library(tidyverse); packageVersion("tidyverse")
library(knitr); packageVersion("knitr")
library(kableExtra); packageVersion("kableExtra")
library(reshape2); packageVersion("reshape2") 
library(vegan); packageVersion("vegan") 
library(phyloseq); packageVersion("phyloseq")
library(FSA); packageVersion("FSA")
library(multcomp); packageVersion("multcomp")
library(multcompView); packageVersion("multcompView")
library(grDevices); packageVersion("grDevices")
library(gratia); packageVersion("gratia")

```  

* r version: `r getRversion()`
* RStudio version: `r rstudioapi::versionInfo()$version`
* r packages:  
  tidyverse, `r packageVersion("tidyverse")`  
  knitr, `r packageVersion("knitr")`  
  kableExtra, `r packageVersion("KableExtra")`  
  vegan, `r packageVersion("vegan")`  
  phyloseq, `r packageVersion("phyloseq")` 
  reshape2, `r packageVersion("reshape2")`
  FSA, `r packageVersion("FSA")`  
  multcomp, `r packageVersion("multcomp")` 
  multcompView, `r packageVersion("multcompView")` 
  grDevices, `r packageVersion("grDevices")` 
  gratia, `r packageVersion("gratia")`
  
### Input files  
Phyloseq objects from script 'patch-normalization-transformation-18s.Rmd' 

```{r import phyloseq object}
#input phyloseq object with raw, transformed sequence counts
phy.2 <- readRDS("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/norm_transform/objects/phy.2.rds")

```

### Format files  
```{r format & transform data 1}
#convert phyloseq object into data.frame
df.rw <- psmelt(phy.2)

# Use the dcast function to reshape the dataframe
a <- dcast(df.rw, Sample ~ OTU, value.var = "Abundance")

#sample ID to rownames
rownames(a) <- a$Sample

#remove Sample column
a$Sample <- NULL

#convert to matrix
a <- as.matrix(a)

#convert phyloseq object into metadata table - data.frame
m <- as(sample_data(phy.2), "data.frame")

##reorder levels of the factor Patch_type
m$Patch_type <- factor(m$Patch_type, levels=c("colony", "bare"))

##reorder levels of the factor Color
m$Color <- factor(m$Color, levels=c("green", "black", "bare"))

# Get a vector of sample IDs
samples <- unique(m$SampleID)

# Determine number of sequences to use as cut-off for rarefy
raremax <- min(rowSums(a, na.rm = TRUE))

```

```{r calculate alpha diversity metrics, eval = FALSE}
# Initialize a data frame to store iteration results
iteration_results <- data.frame()

# Define samples and raremax
samples <- unique(m$SampleID)
raremax <- min(rowSums(a))

# First Loop: Iterate over each sample ID and perform 1000 iterations
for(sam in samples) {
  # Subset data for the current sample
  sample_data <- a[rownames(a) == sam, , drop = FALSE]
  
  # Iterate 1000 times
  for(i in 1:1000) {
    # Suppress warnings for rarefaction and diversity calculations
    suppressWarnings({
      # Rarefy data
      rarefaction <- rrarefy(sample_data, 155)
      
      # Calculate Richness and Shannon diversity
      richness <- specnumber(rarefaction)
      shannon <- diversity(rarefaction, index = "shannon")
      
      # Calculate Evenness
      evenness <- shannon / log(richness)
    })
    
    # Store results in iteration_results dataframe
    iteration_results <- rbind(iteration_results, data.frame(SampleID = sam, Iteration = i, Richness = richness, Shannon = shannon, Evenness = evenness))
  }
}

# Merge iteration_results with m to add Patch_type
div.res <- merge(iteration_results, m[, c("SampleID", "Patch_type","Color")], by = "SampleID")

# Save model output
saveRDS(div.res, paste0(objects.fp, "/div.res.rds"))

```

```{r input files}
# Load your data (replace 'your_data' with your actual data)
#import R object-
div.res <- readRDS("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/objects/div.res.rds")

```

```{r check output}
# Print iteration results
head(div.res)

```

### Richness 
```{r plot Evenness}
# Create boxplot for richness with facets by Patch_type
ggplot(div.res, aes(x=SampleID, y=Richness)) +
  geom_boxplot(fill="blue", alpha=0.5, width=0.5) +
  labs(title="Boxplot of Average Richness", y="Rarefaction Richness", x="Samples") +
  theme_bw() +
  facet_wrap(~ Patch_type, scales = "free_x", ncol = 3, shrink = TRUE) +
theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))

```

```{r scatterplot richness}
# Create scatterplot
ggplot(div.res, aes(x=Patch_type, y=Richness)) +
  geom_jitter(Patch_type="grey", alpha=0.5, width=0.2) +
  #stat_summary(fun.data=mean_se, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun=mean, geom="point", Patch_type="black", size=3) +
  labs(title="Scatterplot of Richness by patch type", y="Rarefaction Richness", x="patch type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

### Shannon 
```{r plot shannon}
# Create boxplot for Shannon
ggplot(div.res, aes(x=SampleID, y= Shannon)) +
  geom_boxplot(fill="blue", alpha=0.5) +
  labs(title="Boxplot of Average Shannon Diversity Index", y="Shannon Diversity", x="Sample ID") +
  theme_bw() +
  facet_wrap(~ Patch_type, scales = "free_x", ncol = 3, shrink = TRUE) +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))

```

```{r scatterplot Shannon}
# Create scatterplot
ggplot(div.res, aes(x=Patch_type, y=Shannon)) +
  geom_jitter(Patch_type="grey", alpha=0.5, width=0.2) +
  #stat_summary(fun.data=mean_se, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun=mean, geom="point", Patch_type="black", size=3) +
  labs(title="Scatterplot of Shannon by patch type", y="Shannon Diversity", x="patch type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

### Evenness 
```{r plot Evenness}
# Create boxplot for Evenness
ggplot(div.res, aes(x=SampleID, y= Evenness)) +
  geom_boxplot(fill="blue", alpha=0.5) +
  labs(title="Boxplot of Average Evenness Diversity Index", y="Evenness Diversity Index", x="Sample ID") +
  theme_bw() +
  facet_wrap(~ Patch_type, scales = "free_x", ncol = 3, shrink = TRUE) +
  theme(axis.text.x = element_text(size = 8, angle = 45, hjust = 1))

```

```{r scatterplot Evenness}
# Create scatterplot
ggplot(div.res, aes(x=Patch_type, y=Evenness)) +
  geom_jitter(Patch_type="grey", alpha=0.5, width=0.2) +
  #stat_summary(fun.data=mean_se, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun.data=mean_cl_normal, geom="errorbar", Patch_type="black", width=0.2) +
  stat_summary(fun=mean, geom="point", Patch_type="black", size=3) +
  labs(title="Scatterplot of Evenness by patch type", y="Evenness Diversity", x="patch type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

\newpage 
### Are there differences in means between different Patch Types?  
```{r average alpha diversity metrics}
# Initialize a data frame to store mean results
average_results <- data.frame()

# Second Loop: Compute the means for each sample
for(sam in samples) {
  # Subset data for the current sample
  sample_data <- div.res[div.res$SampleID == sam, ]
  
  # Calculate mean Richness, Evenness, and Shannon diversity
  mean_richness <- mean(sample_data$Richness, na.rm = TRUE)
  mean_shannon <- mean(sample_data$Shannon, na.rm = TRUE)
  mean_Evenness <- mean(sample_data$Evenness, na.rm = TRUE)
  
  # Store results in average_results dataframe
  average_results <- rbind(average_results, data.frame(SampleID = sam, 
                                                       Mean.Richness = round(mean_richness, 0),
                                                       Mean.Shannon = round(mean_shannon, 2),
                                                       Mean.Evenness = round(mean_Evenness, 2)))
}

```

```{r add patch info}
# Merge average_results with m to add Patch_type
avg.res <- merge(average_results, m[, c("SampleID", "Patch_type", "Color")], by = "SampleID")

```

```{r check dataframe 2}
#rownames
avg.res.1 <- avg.res %>% 
  column_to_rownames(var = "SampleID")

#re-order/rename columns
avg.res.2 <- avg.res.1 %>%
  dplyr::rename(Patch = Patch_type, Richness = Mean.Richness, Shannon = Mean.Shannon, Evenness = Mean.Evenness) %>%
  dplyr::select(4, 1:3)

#set patch as factor
avg.res.2$Patch <- as.factor(avg.res.2$Patch)

# Print mean results
print(avg.res.2)

```

# Summary Statistics
```{r define functions}
# Function to calculate standard error
standard_error <- function(x) {
  sd(x) / sqrt(length(x))
}

# Function to calculate 95% confidence intervals
confidence_interval <- function(x) {
  se <- standard_error(x)
  mean_x <- mean(x)
  ci <- qt(0.975, df = length(x) - 1) * se
  c(lower = mean_x - ci, upper = mean_x + ci)
}

```

### Richness 
```{r richness average by patch type}
# Group by Soil_Age and summarize with rounded values
avg.soil.age.res.rich <- avg.res.2 %>%
  group_by(Patch) %>%
  summarise(
    n = n(),
    mean = round(mean(Richness, na.rm = TRUE)),
    se = round(standard_error(Richness)),
    ci_lower = round(confidence_interval(Richness)[1]),
    ci_upper = round(confidence_interval(Richness)[2])
  )

# View the resulting dataframe
print(avg.soil.age.res.rich)

```

### Shannon 
```{r shannon average by patch type}
# Group by Soil_Age and summarize with rounded values
avg.soil.age.res.shan <- avg.res.2 %>%
  group_by(Patch) %>%
  summarise(
    n = n(),
    mean = round(mean(Shannon, na.rm = TRUE), 2),
    se = round(standard_error(Shannon), 2),
    ci_lower = round(confidence_interval(Shannon)[1], 2),
    ci_upper = round(confidence_interval(Shannon)[2], 2)
  )

# View the resulting dataframe
print(avg.soil.age.res.shan)

```

### Evenness 
```{r Evenness average by patch type}
# Group by Soil_Age and summarize with rounded values, sample P2.2B has a value of NaN b/c it has a richness of 1 so remove before calculating
avg.soil.age.res.even <- avg.res.2 %>%
  filter(row.names(.) != "P2.2B") %>%
  group_by(Patch) %>%
  summarise(
    n = n(),
    mean = round(mean(Evenness, na.rm = TRUE), 3),
    se = round(standard_error(Evenness), 3),
    ci_lower = round(confidence_interval(Evenness)[1], 3),
    ci_upper = round(confidence_interval(Evenness)[2], 3)
  )

# View the resulting dataframe
print(avg.soil.age.res.even)

```

# Difference in Means? 
## Richness
```{r test diff in means - rich, include = TRUE}
# Extract residuals
t.test.rich <- t.test(Richness ~ Patch, data = avg.res.2)
print(t.test.rich)

```

\newpage 
### Scatterplot 
```{r scatterplot avg. richness}
# Create scatterplot
p.rich <- ggplot(avg.res.2, aes(x= Patch, y= Richness)) +
  geom_boxplot(aes(fill = Patch)) +
  geom_jitter(size= 4, shape= 1, color = "black", width = 0.08) +
  scale_y_continuous(expand = c(0.0, 0.0), limits = c(0, 41), breaks = c(0, 10, 20, 30, 40)) +
  scale_x_discrete(labels = c("colony" = "Colonies", "bare" = "Bare Sediment"), expand = c(0.4, 0.1), drop = FALSE) +
  scale_fill_manual(values= c("#018571", "tan")) + # Patch_type blind friendly palette - RPatch_typeBrewer
  guides(fill = "none") +
  labs(y = "Observed Richness") +
  annotate("text", x = 1, y = 39.5, label = "a", size = 6) +
  annotate("text", x = 2, y = 39.5, label = "b", size = 6) +
  theme_bw() + 
  theme(axis.title.y = element_text(size = 20, face = "bold"), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 18, face = "bold"),
        axis.text.y = element_text(size = 18),
        strip.text.x = element_text(size = 30),
        axis.ticks.x.top = element_blank(),  # Remove tick marks on top
        axis.text.x.top = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.y = element_blank())

#display
p.rich

```

\newpage 
## Shannon 
```{r test diff in means - shan, include = TRUE}
# Extract residuals
t.test.shan <- t.test(Shannon ~ Patch, data = avg.res.2)
print(t.test.shan)

```
 
\newpage 
### Scatterplot 
```{r scatterplot avg. Shannon 1}
# Create scatterplot
p.shan.1 <- ggplot(avg.res.2, aes(x= Patch, y= Shannon)) +
  geom_boxplot(aes(fill = Patch)) +
  geom_jitter(size= 4, shape= 1, Patch_type = "black", width = 0.08) +
  scale_y_continuous(expand = c(0.0, 0.0), limits = c(-0.01, 5.1), breaks = c(0, 1.0, 2.0, 3.0, 4.0, 5.0)) +
  scale_x_discrete(labels = c("colony" = "Colonies", "bare" = "Bare Sediment"), expand = c(0.4, 0.1), drop = FALSE) +
  scale_fill_manual(values= c("#018571", "tan")) + # Patch_type blind friendly palette - RPatch_typeBrewer
  guides(fill = "none") +
  labs(y = "Shannon Diversity") +
  #annotate("text", x = 1, y = 2, label = "a", size = 6) +
  #annotate("text", x = 2, y = 2, label = "a", size = 6) +
  theme_bw() + 
  theme(axis.title.y = element_text(size = 20, face = "bold"), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 18, face = "bold"),
        axis.text.y = element_text(size = 18),
        strip.text.x = element_text(size = 30),
        axis.ticks.x.top = element_blank(),  # Remove tick marks on top
        axis.text.x.top = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.y = element_blank())

#display
p.shan.1

```

\newpage 
```{r scatterplot avg. Shannon 2}
# Create scatterplot
p.shan.2 <- ggplot(avg.res.2, aes(x= Patch, y= Shannon)) +
  geom_boxplot(aes(fill = Patch)) +
  geom_jitter(size= 4, shape= 1, Patch_type = "black", width = 0.08) +
  scale_y_continuous(expand = c(0.0, 0.0), limits = c(0, 3.28), breaks = c(0, 1.0, 2.0, 3.0)) +
  scale_x_discrete(labels = c("colony" = "Colonies", "bare" = "Bare Sediment"), expand = c(0.4, 0.1), drop = FALSE) +
  scale_fill_manual(values= c("#018571", "tan")) + # Patch_type blind friendly palette - RPatch_typeBrewer
  guides(fill = "none") +
  labs(y = "Shannon Diversity") +
  #annotate("text", x = 1, y = 2, label = "a", size = 6) +
  #annotate("text", x = 2, y = 2, label = "a", size = 6) +
  theme_bw() + 
  theme(axis.title.y = element_text(size = 20, face = "bold"), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 18, face = "bold"),
        axis.text.y = element_text(size = 18),
        strip.text.x = element_text(size = 30),
        axis.ticks.x.top = element_blank(),  # Remove tick marks on top
        axis.text.x.top = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.y = element_blank())

#display
p.shan.2

```

\newpage 
## Evenness  
```{r test diff in means - even, include = TRUE}
# Extract residuals
t.test.even <- t.test(Evenness ~ Patch, data = avg.res.2)
print(t.test.even)

```

```{r scatterplot avg. Shannon}
# Create scatterplot
p.even <- ggplot(avg.res.2, aes(x= Patch, y= Evenness)) +
  geom_boxplot(aes(fill = Patch)) +
  geom_jitter(size= 4, shape= 1, Patch_type = "black", width = 0.08) +
 scale_y_continuous(expand = c(0.0, 0.0), limits = c(0.0, 1.05), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1.0)) +
  scale_x_discrete(labels = c("colony" = "Colonies", "bare" = "Bare Sediment"), expand = c(0.4, 0.1), drop = FALSE) +
  scale_fill_manual(values= c("#018571", "tan")) + # Patch_type blind friendly palette - RPatch_typeBrewer
  guides(fill = "none") +
  labs(y = "Pielou Evenness") +
  annotate("text", x = 1, y = 1.02, label = "a", size = 6) +
  annotate("text", x = 2, y = 1.02, label = "b", size = 6) +
  theme_bw() + 
  theme(axis.title.y = element_text(size = 20, face = "bold"), 
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 18, face = "bold"),
        axis.text.y = element_text(size = 18),
        strip.text.x = element_text(size = 30),
        axis.ticks.x.top = element_blank(),  # Remove tick marks on top
        axis.text.x.top = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.y = element_blank())

#display
p.even

```

####Objects as .rds files 
```{r save objects}
#average alpha diversity values per sample
saveRDS(avg.res.2, paste0(objects.fp, "/avg.res.2.rds"))

#richness scatterplot
saveRDS(p.rich, paste0(objects.fp, "/p.rich.rds"))

#shannon scatterplot
saveRDS(p.shan.1, paste0(objects.fp, "/p.shan.1.rds"))

#shannon scatterplot
saveRDS(p.shan.2, paste0(objects.fp, "/p.shan.2.rds"))

#Evenness scatterplot
saveRDS(p.even, paste0(objects.fp, "/p.even.rds"))

```

###Save Files 
```{r save combined summary stats}
#check and set working directory
setwd("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/output/stats/Patch_type")
getwd()

#move rownames to column sampleID
avg.res.3 <- avg.res.2 %>%
  rownames_to_column(var = "SampleID")

#save summary statistics
write.csv(avg.res.3, "patch-alpha-diversity-18s-by-sample.csv", row.names = FALSE)

#save summary statistics
write.csv(avg.soil.age.res.rich, "Richness_18s_summary_stats.csv", row.names = FALSE)

#save summary statistics
write.csv(avg.soil.age.res.shan, "Shannon_18s_summary_stats.csv", row.names = FALSE)

#save summary statistics
write.csv(avg.soil.age.res.even, "Evenness_18s_summary_stats.csv", row.names = FALSE)

#save pairwise comparisons
# Save richness the results as a CSV file
capture.output(print(t.test.rich), file = "Richness_18s_tTest.txt")

#shannon
capture.output(print(t.test.shan), file = "Shannon_18s_tTest.txt")

#Evenness
capture.output(print(t.test.even), file = "Evenness_18s_tTest.txt")

```

```{r save rich figures, include = FALSE}
#check and set working directory
setwd("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/output/plots/Patch_type/")
getwd()

#richness
#save plot as pdf
pdf("richness-18s-rarefied-155.pdf",         # File name
    width =11, height = 8.5, # Width and height in inches
    bg = "white",          # Background Patch_type
    colormodel = "cmyk",  # Patch_type model (cmyk is required for most publications)
    paper = "USr")          # Paper size-- portrait: a4", "letter", "legal" (or "us") | landscape: "a4r" and "USr"

#plot
p.rich

# Closing the graphical device
dev.off() 

##save pdf
cairo_pdf("richness-18s-rarefied-155-II.pdf", width = 11, height = 8.5, family = "Helvetica")

##plot to save
p.rich

##Closing the graphical device
dev.off()

#Save as jpg
jpeg(filename = "richness-18s-rarefied-155.jpeg", 
     width = 1000, 
     height = 600, 
     units = "px", 
     pointsize = 12, 
     quality = 100, 
     bg = "white", 
     res = NA)

#plot
p.rich

# Close device
dev.off()

#save as .svg file
ggsave("richness-18s-rarefied-155.svg", plot = p.rich, device = "svg", width = 11, height = 8.5, units = "in")

```

```{r save shan 1 figures}
#check and set working directory
setwd("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/output/plots/Patch_type/")
getwd()

#shannon
#save plot as pdf
pdf("shannon-1-18s-rarefied-155.pdf",         # File name
    width =11, height = 8.5, # Width and height in inches
    bg = "white",          # Background Patch_type
    colormodel = "cmyk",  # Patch_type model (cmyk is required for most publications)
    paper = "USr")          # Paper size-- portrait: a4", "letter", "legal" (or "us") | landscape: "a4r" and "USr"

#plot
p.shan.1

# Closing the graphical device
dev.off() 

##save pdf
cairo_pdf("shannon-1-18s-rarefied-155-II.pdf", width = 11, height = 8.5, family = "Helvetica")

##plot to save
p.shan.1

##Closing the graphical device
dev.off()

#Save as jpg
jpeg(filename = "shannon-1-18s-rarefied-155.jpeg", 
     width = 1000, 
     height = 600, 
     units = "px", 
     pointsize = 12, 
     quality = 100, 
     bg = "white", 
     res = NA)

#plot
p.shan.1

# Close device
dev.off()

#save as .svg file
ggsave("shannon-1-18s-rarefied-155.svg", plot = p.shan.1, device = "svg", width = 11, height = 8.5, units = "in")

```

```{r save shan 2 figures}
#check and set working directory
setwd("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/output/plots/Patch_type/")
getwd()

#shannon
#save plot as pdf
pdf("shannon-2-18s-rarefied-155.pdf",         # File name
    width =11, height = 8.5, # Width and height in inches
    bg = "white",          # Background Patch_type
    colormodel = "cmyk",  # Patch_type model (cmyk is required for most publications)
    paper = "USr")          # Paper size-- portrait: a4", "letter", "legal" (or "us") | landscape: "a4r" and "USr"

#plot
p.shan.2

# Closing the graphical device
dev.off() 

##save pdf
cairo_pdf("shannon-2-18s-rarefied-155-II.pdf", width = 11, height = 8.5, family = "Helvetica")

##plot to save
p.shan.2

##Closing the graphical device
dev.off()

#Save as jpg
jpeg(filename = "shannon-2-18s-rarefied-155.jpeg", 
     width = 1000, 
     height = 600, 
     units = "px", 
     pointsize = 12, 
     quality = 100, 
     bg = "white", 
     res = NA)

#plot
p.shan.2

# Close device
dev.off()

#save as .svg file
ggsave("shannon-2-18s-rarefied-155.svg", plot = p.shan.2, device = "svg", width = 11, height = 8.5, units = "in")

```

```{r save evenness figures, include = FALSE}
#check and set working directory
setwd("F:/Projects/Sunspears/Studies/Patch_Schmidt-et-al/analyses/amplicons/18s/alpha_diversity/output/plots/Patch_type/")
getwd()

#evenness
#save plot as pdf
pdf("evenness-18s-rarefied-155.pdf",         # File name
    width =11, height = 8.5, # Width and height in inches
    bg = "white",          # Background Patch_type
    colormodel = "cmyk",  # Patch_type model (cmyk is required for most publications)
    paper = "USr")          # Paper size-- portrait: a4", "letter", "legal" (or "us") | landscape: "a4r" and "USr"

#plot
p.even

# Closing the graphical device
dev.off() 

##save pdf
cairo_pdf("evenness-18s-rarefied-155-II.pdf", width = 11, height = 8.5, family = "Helvetica")

##plot to save
p.even

##Closing the graphical device
dev.off()

#Save as jpg
jpeg(filename = "evenness-18s-rarefied-155.jpeg", 
     width = 1000, 
     height = 600, 
     units = "px", 
     pointsize = 12, 
     quality = 100, 
     bg = "white", 
     res = NA)

#plot
p.even

# Close device
dev.off()

#save as .svg file
ggsave("evenness-18s-rarefied-155.svg", plot = p.even, device = "svg", width = 11, height = 8.5, units = "in")

```

#End of Script 